The universal property of direct integrals in W$^*$-categories

### 2018-10-25 direct_integrals.tex
Andre Henriques stacky suggestion

\thanks{\textit{Acknowledgements.} Part of this work was conducted while the first author was at the Max Planck Institute for Mathematics in the Sciences in Leipzig, Germany.}

@@

>>>>

\thanks{\textit{Acknowledgements.} Part of this work was conducted while the first author was at the Max Planck Institute for Mathematics in the Sciences in Leipzig, Germany. We thank Andr\'e{} Henriques for useful discussions.}

@@

\todo[inline]{$L^\infty(X,\cat{C})$ is pseudo-functorial in $X$. Does the resulting fibration satisfy interesting descent conditions? (Suggestion due to Andr\'e{} Henriques on MO.)}
